Analysis and Figures for Gallego et al, 2020

### 2020-09-04 Manuscript/What.lies.ahead.reviewed.tex
Wilcoxon with proper richness

Given the sea-surface temperatures and pH values for 2017 (observed) and 2095 (estimated) and taxon-specific logistic regression models, we then evaluated the suitability of habitat for each taxon in the future scenario. For each point in the pH - temperature grid, we calculated a species' probability of presence as the mean of 100 independent draws of the posterior model response. We estimated species richness as the sum of taxa with $>$ 50\% probability of occurrence at a given set of environmental parameters.

>>>>

Given the sea-surface temperatures and pH values for 2017 (observed) and 2095 (estimated) and taxon-specific logistic regression models, we then evaluated the suitability of habitat for each taxon in the future scenario. For each point in the pH - temperature grid, we calculated a species' probability of presence as the mean of 100 independent draws of the posterior model response. {\color{red} For richness estimations in future scenarios, we used each of the 100 draws of the posteriors in each environmental point as a sample and tallied the number of species detected on each draw. The mean value across the 100 draws was the input for a Wilcoxon test of differences in species richness between the 2017 and 2095 scenarios in each region. We performed the Wilcoxon test globally (total species richness) and on each phylum independently }

### 2020-09-04 Scripts/Manuscript.Main.Analysis.Rmd
Wilcoxon with proper richness

Using a global ANOVA to see if there are differences between Years (2095-2017) in both Areas. Then a  wilcoxon test to see if there is a difference  on each phylum
```{r}

@@

input.for.left %>% 
  mutate(sim.row = rep(1:10873, n_distinct(taxa))) -> input.richness

input.richness %>% 
  nest(-Area) %>% 
  mutate(data = map (data, ~ .x %>% 
                         group_by(Year,  sim.row) %>% 
                         summarise( Richness = sum(present)) ),
         lm = map(data, ~ lm(Richness ~ Year, data = .x)),
         tidy_lm = map(lm, broom::tidy)) %>%
  unnest(tidy_lm)

input.richness %>% 
  nest(-phylum,) %>% 
  #  slice(1) %>%
    mutate(data = map (data, ~ .x %>% 
                         group_by(Year,  sim.row) %>% 
                         summarise( Richness = sum(present)) )) %>% 
   mutate(wilcoxon = map (data, ~ wilcox.test(Richness ~ Year, data = .x) ))  -> results.lm

>>>>

First calculate the richness in each point as following. In each environmental point, the 100 draws represent if a taxa was found or not. We sum the draws of all taxa so we have 100 estimation of richness for each point - we then take the mean of those 100 draws and we have a estimation of richness at that point.

```{r get the richness per phylum}

split.matrices.by.taxa <- list()

for (i in 1:n_distinct(expanded.future$taxa)){
  start.col = 1 + (i-1)*10873
  fin.col = start.col + 10872

  split.matrices.by.taxa[[i]] <- posterior.predict.all.taxa[,start.col:fin.col]
  }

richness.fun <- function(x) {
    Reduce('+', x) 
    }

distinct(expanded.future,taxa) %>% 
  mutate(draws = split.matrices.by.taxa) %>% 
  left_join(phylum.info %>% select(taxa, phylum)) %>% 
  group_by(phylum) %>% 
  summarise(draws =  Reduce('+',draws)) -> richness.by.draw.by.phylum.by.point

 richness.by.draw.by.phylum.by.point %>% 
   nest() %>% 
   mutate(data = map (data, function(.x) colMeans(as.matrix(.x)) %>% 
                        as_tibble %>% 
                        rownames_to_column("sim.row"))) %>% 
   unnest()-> richness.by.phylum.by.point

 expanded.future %>%
   ungroup() %>% 
   slice (1:10873) %>% 
   rownames_to_column("sim.row") %>% 
   select(Area, Year, sim.row) %>% 
   right_join(richness.by.phylum.by.point) -> richness.by.phylum.by.point

Now the Global - richness by point

```{r}
distinct(expanded.future,taxa) %>% 
  mutate(draws = split.matrices.by.taxa) %>% 
  summarise(draws =  Reduce('+',draws)) -> richness.by.draw.by.point

richness.by.draw.by.point %>% 
   nest() %>% 
   mutate(data = map (data, function(.x) colMeans(as.matrix(.x)) %>% 
                        as_tibble %>% 
                        rownames_to_column("sim.row"))) %>% 
   unnest()-> richness.by.point

expanded.future %>%
   ungroup() %>% 
   slice (1:10873) %>% 
   rownames_to_column("sim.row") %>% 
   select(Area, Year, sim.row) %>% 
   right_join(richness.by.point) -> richness.by.point
```

Because we are comparing two 
```{r}

@@

richness.by.point %>% 
  nest(-Area) %>% 
  mutate(wilcoxon = map(data, ~ wilcox.test(value ~ Year, data = .x)),
         tidy_wilcox = map(wilcoxon, broom::tidy)) %>%
  pull(wilcoxon)

## We cannot

richness.by.phylum.by.point %>% 
   nest(-phylum,-Area) %>% 
   mutate(wilcoxon = map (data, ~ wilcox.test(value ~ Year, data = .x) ))  -> results.lm
